Legacy Data Confounds Modern Genomics Studies

### 2019-03-24 PlottingScripts/ProcessPlotData.Rmd
update

#AddGenotypes
for f in `seq 1 22`;
do echo $f;
bcftools view -R $DataPath/Significant_Positions.txt \
$RawDataPath/ALL.chr${f}$VCF \
| grep -v "^#" \
>> $DataPath/Significant_Positions.vcf ; \
done

@@

/Users/luke/bin/plink_mac/plink \
--vcf $DataPath/Significant_Positions.recode.vcf \
--recode \
--out $DataPath/Significant_Positions

```
```{r}
data_bim <- fread(paste0(DataPath,
                         'Significant_Positions.bim'), 
                  col.names = c('Chr','rsID','X',
                                'Pos','Ref','Alt')) %>%
  select(rsID)

@@

```

##Compare Over and Under Qual 30
```{r}
#read Genotypes
GT = fread(paste0(DataPath,
                   'SigVar_Pop_0.01_rsID.genotype.txt'))
ColNames = read.table(paste0(DataPath,
                   'ColNames_rsID.txt'), 
                   header=F)

names(GT) = as.character(unlist(ColNames))
names(GT)[4] = 'rsID'
GT$ID <- as.numeric(as.character(GT$ID))

Sig.rsID <- fread(paste0(DataPath,
                         'SignificantVariants.txt'), 
                  col.names = c('Chr','Pos','rsID', 
                                'ID', 'dev', 'log10_p'))
##Compare over and under 30

mGT = melt(unique(GT), 
           id = c('Chr','Pos',
                  'ID','rsID'))
mGT = merge(unique(bas_dt[,
                          c('sample',
                            'Population',
                            'avg_qual')]), 
            mGT, 
            by.x='sample',
            by.y='variable')

mGT = merge(mGT, 
            Sig.rsID, 
            by=c('Chr','Pos',
                 'ID','rsID'))

over30 = mGT[which(mGT$avg_qual > 30),]

under30 = mGT[which(mGT$avg_qual < 30),]

o30AF <- 
		over30 %>% 
		group_by(Chr,Pos,
		         ID,rsID) %>% 
		summarize(oAF = sum(value))

u30AF <- 
		under30 %>% 
		group_by(Chr,Pos,
		         ID,rsID) %>% 
		summarize(uAF = sum(value))

AF30 <- merge(u30AF, 
              o30AF, 
              by=c('Chr','Pos',
                   'ID','rsID'))

>>>>

#AddGenotypes
for f in `seq 1 22`;
do bcftools view \
-R $DataPath/Significant_Positions.txt \
$RawDataPath/ALL.chr${f}$VCF \
| grep -v "^#" \
>> $DataPath/Significant_Positions.vcf ; \
done

@@

/Users/luke/bin/plink_mac/plink \
--vcf $DataPath/Significant_Positions.recode.vcf \
--make-bed \
--out $DataPath/Significant_Positions

```
##Compare Over and Under Qual 30
```{r}
data_bim <- fread(paste0(DataPath,
                         'Significant_Positions.bim'), 
                  col.names = c('Chr','rsID','X',
                                'Pos','Ref','Alt')) %>%
  select(rsID)

@@

##Compare over and under 30

mGT = melt(unique(data_genotype), 
           varnames = c('rsID','sample'), 
           value.name = 'Genotype')

mGT = merge(unique(bas_dt[,
                          c('sample',
                            'Population',
                            'avg_qual')]), 
            mGT, 
            by = 'sample')

over30 = unique(mGT[which(mGT$avg_qual > 30),])

under30 = unique(mGT[which(mGT$avg_qual < 30),])

o30AF <- 
		over30 %>% 
		group_by(rsID) %>% 
		summarize(oAF = sum(Genotype))

u30AF <- 
		under30 %>% 
		group_by(rsID) %>% 
		summarize(uAF = sum(Genotype))

AF30 <- merge(u30AF, 
              o30AF, 
              by=c('rsID'))
